---
title: "The basic R Markdown"
author: "JDW"
date: "2024-08-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Data description:

**Description of the data and variables.**

The data used in this lab is salaries.csv. It contains academic ranks for men and women and their salaries. You will find more information about the data at: [Salary Data](https://rpubs.com/LeeLee00/896557)

- rank: Academic title
- discipline: A or B
- yrs.since.phd: Number of years
- yrs.service: Number of years
- sex: Male, or Female
- salary: Annual salary

# Data wrangling:

This is how the data has been changed to create a new grouping.

- Read: Read the csv file
- Select: Select 4 columns from the data frame
- Filter: Remove any rows where the salary is NA
- Group_by: Group by 3 columns
- Count: Count the number of rows of grouped columns
```{r library, results='hide',message=FALSE, echo=TRUE, warning=FALSE}
#Data Wrangling in R
#John Williams

#Load library
library(tidyverse)
#Set working directory
setwd("~/GitHub/DSCI605")
```


```{r salaries, results='hide', echo=TRUE, message=FALSE, warning=FALSE}
#Load the dataset
salaries <- read_csv("salaries.csv")

#Create new groups from the data frame
new_groups <- salaries %>% 
  select(rank, discipline, sex, salary) %>% #Select 4 columns from the data frame
  filter(!is.na(salary)) %>%   #Remove any rows where the salary is NA
  group_by(rank, discipline, sex) %>%  #group by 3 columns
  count(name = "tally")   #Count the number of rows of grouped columns

wide <- new_groups %>% #convert the data frame to the wide format
  spread(sex, tally, fill = NA, convert = FALSE, drop = TRUE, sep = NULL)   #Convert the data frame to the wider format using
                                #names from "sex" for new columns and values from "tally"

long <- wide %>% 
  gather("sex", "n", Male, Female,  na.rm = TRUE, convert = FALSE, factor_key = FALSE) %>%  #Reformat to long format
  arrange(rank, sex)   #Rearrange the data frame to sort by rank and then sex
```

