---
title: "The basic R Markdown"
author: "JDW"
date: "2024-08-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Data description:

**Description of the data and variables.**

The data used in this lab is salaries.csv. It contains academic ranks for men and women and their salaries. You will find more information about the data at: [Salary Data](https://rpubs.com/LeeLee00/896557)

- rank: Academic title
- discipline: A or B
- yrs.since.phd: number of years
- yrs.service: number of years
- sex: Male, or Female
- salary: Annual salary

# Data wrangling:

This is how the data has been changed.

- Read: Read the csv file
- Select: Select 4 columns from the data frame
- Filter: Remove any rows where the salary is NA
- Group_by: Group by 3 columns
- Count: Count the number of rows of grouped columns
```{r library, results='hide',message=FALSE, echo=FALSE, warning=FALSE}
library(tidyverse)
```


```{r salaries, results='hide', echo=TRUE, message=FALSE, warning=FALSE}

salaries <- read.csv("salaries.csv")

new_groups <- salaries %>% 
  select(rank, discipline, sex, salary) %>%
  filter(!is.na(salary)) %>%
  group_by(rank, discipline, sex) %>%
  count(name = "tally")
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
