---
title: "RMarkdown1"
author: "JDW"
date: "2024-08-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

### Markdown sections

This lab will use the data provided: salaries.csv to make a R Markdown file.

### Link
Let me add a link
[BSU](http://www.bsu.edu)

### List
1. Topic A
2. Topic B<br>
  +Subtopic B1<br>
  +Subtopic B2
3. Topic C

# Headings
## Heading 2
### Heading 3

![Adding an image](C:\Users\jowilli1\Pictures\RLang.jfif)

*italics* and **bold**<br>
inline equation: $A = \pi*r^{2}$



## Code chunks
```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
```

```{r Salary data, results='hide', message=FALSE}
#Import data from a comma delimited file
Salaries <- read_csv('salaries.csv')
```
Hide the code
```{r, echo=FALSE}
1 + 1
```
See the code and print results.
```{r, echo=TRUE}
1 + 1
```
Hide the print output
```{r, results=FALSE}
summary(cars)
```

* Hide messages:
```{r, message=FALSE}
message("You will not see the message.")
```

* Hide messages:
```{r, message=TRUE}
library(tidyverse)
```

* Hide warning messages:
```{r, warning=FALSE}
#This will generate a warning but it will be suppressed
1:2 + 1:3
```

## Including Plots

Hide code, but show the plot<br>
```{r pressure0, echo=FALSE}
plot(pressure)
```

Show the code but hide the plot
```{r pressure1, echo=TRUE, fig.show="hide"}
plot(pressure)
```

### Summary
<!-- This text will be hidden -->
<!-- We can hide multiple lines
of text all day long. -->
#### Hide information in code chunk
* Hiding code:                        echo = FALSE
* Hide both code and its output:      include = FALSE
* Hide output:                        results = FALSE
* Hide image:                         fig.show='hide'
You can also embed plots, for example:

```{r Salaries, echo=FALSE}
hist_data <- hist(Salaries$salary, plot = FALSE)
plot(hist_data,
     main = "Histogram of Salary",
     xlab = "Salary",
     ylab = "Frequency",
     col = "lightblue",
     border = "black")

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
