---
title: "JohnWilliams_6.3_GroupHistogram"
author: "JDW"
date: "2024-09-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Group Histogram

This is documentation for creating group histograms.  There are two example plots.

## Load Packages

```{r packages, echo=TRUE,results='hide', message=FALSE}
library(tidyverse)
if (!require(colorspace))  {install.packages(colorspace)}; require(colorspace)

setwd("~/GitHub/DSCI605/Mod6")
```

## Load data

```{r load data, echo=TRUE, results='hide', message=FALSE}
df <- read.csv("Sampledata2.csv")

df
```

## Create a new column

The new column that shows Low, Medium and High values for CrimeRates based on 
ranges in CrimeRates.  Make sure the new column is a factor.
```{r addColumn, echo=TRUE, results='show', message=TRUE}

df <- df %>%
  select(Year, CrimeRate) %>%
  mutate(RangeGroup = case_when(CrimeRate < 250 ~ 'small',
                          CrimeRate >= 250 & CrimeRate <= 500 ~ 'medium',
                          CrimeRate > 500 ~ 'large'))

# Reorder RangeGroup factor levels in the desired order
df$RangeGroup <- factor(df$RangeGroup, levels = c("small", "medium", "large"))
head(df)
```

## Create Color Options

Colors are needed for Years and the three RangeGroup values.

```{r establishColors}
n <- length(unique(df$Year))
col1=colorspace::diverge_hcl(n)
# Define colors in the same order as the factor levels
col2 <- c("blue", "green", "red")
```

## Including 2 Plots

Color changes based on "Year".

```{r plot1, echo=TRUE}
df %>% filter(Year %in% c(2013:2018)) %>%
  ggplot(aes(x=CrimeRate, color=as.factor(Year), fill=as.factor(Year))) + #continuous value
  geom_histogram(position="dodge", alpha=0.5, bins=10) +
  scale_color_manual(values=col1) +
  scale_fill_manual(values=col1) +
  labs(title="Crime Rate Histogram Plots", x="Crime Rate per 100, 1000 people", y="Count") +
  labs(fill = 'Year') +
  guides(color = "none") +
  theme_classic()
```

Color changes based on Range Group.
```{r plot2, echo=TRUE}
df %>% 
  ggplot(aes(x=CrimeRate, color=RangeGroup, fill=RangeGroup)) + #continuous value
  geom_histogram(position="dodge", alpha=0.5, bins=10) +
  scale_color_manual(values=col2) +
  scale_fill_manual(values=col2, labels = c("CrimeRate < 250", "250 <= CrimeRate <= 500", "CrimeRate > 500")) +
  labs(title="Crime Rate Histogram Plots", x="Crime Rate per 100, 1000 people", y="Count") +
  labs(fill = 'Year') +
  guides(color = "none") +
  theme_classic()
```